Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Added caption of a figure.

Let~$v\in V_{\bar Q}$.  If~$v$ corresponds to a finite maximal path of~$\bar Q\blossom$, then the situation around~$v$ is as follows:

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
	\caption{.}
	\label{fig:stars}
\end{figure}

If~$v$ corresponds to an infinite maximal path, then the situation around~$v$ is as follows:

\vincent{Change formulation here to have the pictures on the same line.}

@@

Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ aare dual to each other.
\end{proof}

@@

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{orderCurves}}
	\caption{The order~$\prec_\alpha$ is given by the order in which the curve cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

>>>>

Let~$v\in V_{\bar Q}$. The situation around~$v$ is as follows, depending on whether~$v$ corresponds to a finite or infinite maximal path of~$\bar Q\blossom$,:

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{halfStar} \qquad \includegraphics[scale=.7]{star}}
	\caption{The situation around~$v$ (green vertex). On the left,~$v$ corresponds to a finite maximal path of~$\bar Q$, while on the right,~$v$ corresponds to an infinite one.}
	\label{fig:stars}
\end{figure}

@@

Moreover, by construction, each edge of~$\dissection_{\bar Q}$ which is not on the boundary of~$\surface(\bar Q)$ crosses exactly one edge of~$\dissection_{\bar Q}\dual$, and vice versa.
This shows that~$\dissection_{\bar Q}$ and~$\dissection_{\bar Q}\dual$ are dual to each other.
\end{proof}

@@

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{orderCurves}}
	\caption{The order~$\prec_\alpha$ is given by the order in which the curves cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}
